Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-15 README.Rmd
fixed an issue with the data descriptions

- `r names(bullet_train)[1]` = ID number associated with the bullet-land signature comparison
- `r names(bullet_train)[2]` = ID associated with the first bullet-land in the comparison. The format is 'study-barrel number-bullet number-land number'.
- `r names(bullet_train)[3]` = ID associated with the second bullet-land in the comparison. Again, the format is 'study-barrel number-bullet number-land number'.
- `r names(bullet_train)[4]`, `r names(bullet_train)[5]`, `r names(bullet_train)[6]`, `r names(bullet_train)[7]`, `r names(bullet_train)[8]`, `r names(bullet_train)[9]`, `r names(bullet_train)[10]`, `r names(bullet_train)[11]`, and `r names(bullet_train)[12]` = comparison features of the two bullet-land signatures. See XXX for definitions of these features.
- `r names(bullet_train)[13]` = indicator variable specifying whether the two bullet-lands are a match
- `r names(bullet_train)[14]` = the random forest score associated with the comparison in support of a match

@@

A dataset with `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from sets 1 and 11 of the Hamby 224 Clone sets (XXX reference XXX). Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet. Each bullet has 6 lands. The data contains comparisons of bullet-lands within a set. With three bullets with six lands per set, there are a total of (2 sets) x (3! bullet comparisons) x (6^2 land comparisons) = `r 2 * (3 + 2 + 1) * 6^2` comparisons. However, there are only `r dim(bullet_test)[1]` comparisons in the `bullet-test` data. This is due to the fact that some of the lands are missing from the data (probably due to tank rank): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11. The `r dim(bullet_test)[2]` variables in the data are the same as those in the training data (see the variable definitions associated with `bullet-train`).

>>>>

- `r names(bullet_train)[1]` = ID number associated with the bullet-land signature comparison
- `r names(bullet_train)[2]` = ID associated with the first bullet-land in the comparison. The format is 'study - barrel number - bullet number - land number'
- `r names(bullet_train)[3]` = ID associated with the second bullet-land in the comparison. Again, the format is 'study - barrel number - bullet number - land number'
- `r names(bullet_train)[4]`, `r names(bullet_train)[5]`, `r names(bullet_train)[6]`, `r names(bullet_train)[7]`, `r names(bullet_train)[8]`, `r names(bullet_train)[9]`, `r names(bullet_train)[10]`, `r names(bullet_train)[11]`, and `r names(bullet_train)[12]` = comparison features of the two bullet-land signatures. See XXX for definitions of these features
- `r names(bullet_train)[13]` = indicator variable specifying whether the two bullet-lands are a match
- `r names(bullet_train)[14]` = the random forest score associated with the comparison in support of a match

@@

A dataset with `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from sets 1 and 11 of the Hamby 224 Clone sets (XXX reference XXX). Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet. Each bullet has 6 lands. The data contains comparisons of bullet-lands within a set. With three bullets with six lands per set, there are a total of (2 sets) x (3! bullet comparisons) x (6^2 land comparisons) = `r 2 * (3 + 2 + 1) * 6^2` comparisons. However, there are only `r dim(bullet_test)[1]` comparisons in the `bullet-test` data. This is due to the fact that some of the lands are missing from the data (probably due to tank rank): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11. The variables in the data are as follows:

- `r names(bullet_test)[1]` = ID number associated with the bullet-land signature comparison
- `r names(bullet_test)[2]` = ID associated with the first bullet-land in the comparison with a format of 'study - set number - bullet number - land number'
- `r names(bullet_test)[3]` = ID associated with the second bullet-land in the comparison with a format of 'study - set number - bullet number - land number'
- `r names(bullet_test)[4]`, `r names(bullet_test)[5]`, `r names(bullet_test)[6]`, `r names(bullet_test)[7]`, `r names(bullet_test)[8]`, `r names(bullet_test)[9]`, `r names(bullet_test)[10]`, `r names(bullet_test)[11]`, and `r names(bullet_test)[12]` = comparison features of the two bullet-land signatures. See XXX for definitions of these features.
- `r names(bullet_test)[13]` = indicator variable specifying whether the two bullet-lands are a match
- `r names(bullet_test)[14]` = the random forest score associated with the comparison in support of a match
